manuscript - APP

### 2018-07-21 R/manuscript_app_alt_clean.Rmd
add kl distance
new ratio

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

@@

@@

```{r echo=F}
# accuracy summarised
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) 
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

@@

>>>>

```{r echo=FALSE}
# Exp 1b
df_exp1b <- 
  readRDS(
    file.path(data_pth, "exp1b", "responses", "responses_150622.rds")) %>% 
  filter(block != 0) %>% as_tibble(.) %>% 
  rename(targetk = type) %>% mutate(id = factor(subject)) %>% 
  mutate(contrast_abs = abs(log2(targetk / restk)), 
         target_straight = (targetk > restk),
         ratio = (besselI(targetk,0) * exp(targetk)) / (besselI(restk,0) * exp(restk)),
         ratio_abs = abs(log((besselI(targetk,0) * exp(targetk))) / (besselI(restk,0) * exp(restk))))
participants_exp1b <- 
  read.csv(file.path(data_pth, "exp1b", "participants_150526.csv"), fileEncoding = "UTF8")

@@

```{r kl distance}

ks <- c(2,4,8,16,64)
n <- length(ks)

m <- matrix(rep(0,n*n), ncol = n)
source("tools.R")
for (i in 1:length(ks)) {
  for (j in i:length(ks)) {
    m[i,j] <- kl_distance(ks[i],ks[j])    
  } 
}
rownames(m) <- colnames(m) <- ks

df_kl <- as_data_frame(m) %>%
  mutate(k1 = rownames(m)) %>% 
  gather(k2, value = kl_distance,-k1) %>% 
  mutate(k1 = as.numeric(k1), k2 = as.numeric(k2)) %>% 
  filter(k2>=k1) %>% 
  distinct()

df_kl <- df_kl %>% bind_rows(df_kl %>% mutate(tmp =k1, k1=k2,k2=tmp) %>% select(-tmp))

df_exp1b <- df_exp1b %>% 
  left_join(df_kl, by = c("targetk"="k1","restk"="k2"))
```

@@

```{r echo=F}
# accuracy summarised
accu_summary <- df_exp1b %>% 
  mutate(contrast_abs_f = as.character(contrast_abs)) %>% 
  group_by(id, contrast_abs, contrast_abs_f, target_straight, kl_distance,ratio,ratio_abs) %>% 
  dplyr::summarise(accu = mean(accuracy), n = n()) %>% 
  ungroup()
accu_summary_wo_0 <- accu_summary %>% filter(contrast_abs > 0)

@@

```{r Charts1b kl distance}
#accu_summary %>% 
#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
#  geom_jitter() 
accu_summaryx %>% 
  ggplot(
    aes(x = kl_distance, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +

  theme(aspect.ratio = 1) + 
  xlab("kl distance") + ylab("Accuracy")
```

```{r Charts1b ratio}
#accu_summary %>% 
#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
#  geom_jitter() 
accu_summaryx %>% 
  ggplot(
    aes(x = ratio, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +

  theme(aspect.ratio = 1) + 
  xlab("kl distance") + ylab("Accuracy") +scale_x_log10()
```

```{r Charts1b ratio abs}
#accu_summary %>% 
#  ggplot(aes(x = contrast_abs, y = accu, colour = target_straight)) + 
#  geom_jitter() 
accu_summaryx %>% 
  ggplot(
    aes(x = ratio_abs, y = accu, 
        group = target_straight, shape = target_straight, linetype = target_straight)) + 
  stat_summary(fun.data = "mean_cl_boot", alpha = .5) +
  stat_summary(fun.y = "mean", alpha = .5, geom = "line") +

  theme(aspect.ratio = 1) + 
  xlab("kl distance") + ylab("Accuracy") +scale_x_continuous(trans ="log")
```
